---
title: "C16_lecture"
author: "John Doe"
date: "3/14/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

# Handling Text with `stringr` Package

### 

-   Hands-on Assignment starts from line 29.
-   Have enough time and run the codes using RStudio before doing Hands-on Assignment
-   When you want to run code, please use `ctrl + Enter` instead of a mouse

### 

# Run these two lines first

```{r}
if (!require('tidyverse')) install.packages('tidyverse'); library('tidyverse') 
if (!require('stringr')) install.packages('stringr'); library('stringr') 
```

# Create strings using quotation marks

```{r}
#double quotation marks

yolo <- "You only live once, but if you do it right, once is enough"
```

```{r}
print(yolo)
```

```{r}
#single quotation marks

single <- 'To put a "quote" inside a string, use single quotes'
```

```{r}
#data type check

class(single)

typeof(single)
```

# Multiple strings using `c()`

```{r}
c("You", "only", "live", "once")
```

# Count string length using `str_length()`

```{r}
str_length(yolo)
```

# String combination with `str_c()`

```{r}
str_c("You", "only", "live", "once")
```

# String combination with a `sep` operator

```{r}
str_c("You", "only", "live", "once", sep = ", ")
```

# From multiple strings to a single string

```{r}
str_c("You", "only", "live", "once", collapse = ", ")
```

# String slicing using `str_sub()`

```{r}
capital <- c("YOU", "ONLY", "LIVE", "ONCE")

str_sub(capital, 1, 3)
```

# String modification using `str_to_lower()`

```{r}
str_sub(capital, 1, 1) <- str_to_lower(str_sub(capital, 1, 1))

print(capital)
```

# String modification using `str_to_upper()`

```{r}
small <- c("you", "only", "live", "once")

str_sub(small, 1, 2) <- str_to_upper(str_sub(small, 1, 2))

print(small)
```

# String sort from A to Z using `str_sort()`

```{r}
food <- c("egg", "snack", "apple")

str_sort(food)
```

# Concatenate a series of strings using `paste` & `paste0`

```{r}
# First example

time <- paste("Time", "is", "money")

print(time)
```

```{r}
#instead of two lines of the previous chunk (First example)

(time <- paste("Time", "is", "money"))
```

```{r}
# `sep` parameter

paste("Time", "is", "money", sep = "_")
```

```{r}
# `sep` parameter

paste("Time", "is", "money", sep = "")
```

```{r}
# Difference between `collapse` and `sep` parameter 

paste("1st", "2nd", "3rd", collapse = ", ")

paste("1st", "2nd", "3rd", sep = ", ")
```

```{r}
# `paste0` function 

paste0("Time", "is", "money")
```
