---
title: "Inclass Assignment (5)"
author: "Akshar Patel"
date: "3/16/2022"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

- If you don't know the answer, leave it blank.
- If you are caught cheating, you will be given minus 50 points.  

### Run this chunk first
```{r}
if (!require('tidyverse')) install.packages('tidyverse'); library('tidyverse') 
```

Q1. Update the author name with your name in YAML part above. 

Q2. A line of code to import a `productivity.csv` file from your `Desktop` folder and assign it as a `productivity` variable.
```{r}
productivity <- read_csv("C:/Users/Akshar/Desktop/Inclass_Assigment_5/productivity.csv")
```

Q3. What is the number of rows and columns of `productivity` variable? 
```{r}
#Rows: 1192
#Columns: 6
```

Run this chunk for Q4
```{r}
ages <- data.frame(Name = c("Jane", "William", "Ben", "Jaewan"),
                   Age = c(31, 23, 12, 42))
```

Q4. A line of code to save `ages` dataframe to your `Desktop` folder as `ages.csv`. You don't need to submit `ages.csv` to Canvas.
```{r}
write_csv(ages, "C:/Users/Akshar/Desktop/Inclass_Assigment_5/ages.csv")
```

Run this code for Q5.
```{r}
if (!require('readxl')) install.packages('readxl'); library('readxl') 
```

Q5. A line of code to import a `scale.xlsx` file and store it as a `scale` variable from your `Desktop` folder.
```{r}
scale <- read_excel("C:/Users/Akshar/Desktop/Inclass_Assigment_5/scale.xlsx")
```

Q6. Run the following code and answer the reason why it is untidy.
```{r}
table2

#Explanation:  each and every variable must have its own column
```

Q7. Run the following code and answer the reason why it is untidy.
```{r}
table3

#Explanation: Each and every value must have its own cell
```

Q8. Run the following code and answer the reason why it is untidy.
```{r}
table4a

#Explanation: year variable does not exist
```

Q9. Two lines of code that pivots `table4a` as a tidy and longer dataset with the following information. 
- The name of the variable to move the column names to: `year`
- The name of the variable to move the column values to: `cases`
```{r}
table4a %>%
  pivot_longer(c('1999', '2000'), names_to = "year", values_to = "cases")
```

Q10. Two lines of code that pivots `table2` as a tidy and wider dataset with the following information. 
- The column to take variable names from: `type`
- The column to take values from: `count`
```{r}
table2 %>%
  pivot_wider(names_from  = "type", values_from = "count")

```
