---
title: "C18_lecture"
author: "John Doe"
date: "3/21/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

# Handling Date & Time - `lubridate` Package

-   Hands-on Assignment starts from line 25.
-   Have enough time and run the codes using RStudio before doing Hands-on Assignment
-   When you want to run code, please use `ctrl + Enter` instead of a mouse

# Run these three lines first

```{r}
if (!require('tidyverse')) install.packages('tidyverse'); library('tidyverse')
if (!require('lubridate')) install.packages('lubridate'); library('lubridate')
if (!require('nycflights13')) install.packages('nycflights13'); library('nycflights13')
```

# Current date and time

```{r}
# only year and date
today()

#including time
now()
```

# Parsing date from strings

```{r}
# identify the order of year, month, and day in  your  data
# then arrange “y”, “m”, and “d” in the same order

mdy("March 21st 2022")

dmy("31 March 2022")
```

# Parsing time from strings

```{r}
mdy_hms("March/21/2021 11:53:32")
```

# `flights` data preview

```{r}
colnames(flights)
```

# Creating a new column using `make_datetime()` function

```{r}
flights %>%
  select(year, month, day, hour, minute) %>%
  mutate(departure = make_datetime(year, month, day, hour, minute))
```

# Visualize the count of `departure` column

```{r}
flights %>%
  select(year, month, day, hour, minute) %>%
  mutate(departure = make_datetime(year, month, day, hour, minute)) %>%
  ggplot(aes(departure)) +
  geom_freqpoly(binwidth = 86400) # 86400 seconds = 1 day
```

# Pulling out a part of date

```{r}
thatday <- mdy("April 21 1919")

year(thatday)

month(thatday)

month(thatday, label = TRUE)

day(thatday)

wday(thatday)

wday(thatday, label = TRUE, abbr = FALSE)
```

# Visualize the count of `departure` column in terms of day

```{r}
flights %>%
  select(year, month, day, hour, minute) %>%
  mutate(departure = make_datetime(year, month, day, hour, minute)) %>%
  mutate(w_departure = wday(departure, label = TRUE)) %>%
  ggplot(aes(x = w_departure)) + 
  geom_bar()
```

# Time difference as seconds, days, and years

```{r}
today() - ymd("2010/04/14") #Time difference as days

as.duration(today() - ymd("2010/04/14")) #as seconds and years
```

# Convert seconds to period using `seconds_to_period()`

```{r}
diff <- as.duration(ymd_hms("2022/03/18 08:13:33") - ymd_hms("2022/03/14 11:43:32"))

seconds_to_period(diff)
```
