---
title: "C12_lecture"
author: "John Doe"
date: "2/21/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

# Data importing and Tidy data using `tidyverse` package

### 

-   Hands-on Assignment starts from line 28.
-   Have enough time and run the codes using RStudio before doing Hands-on Assignment
-   When you want to run code, please use `ctrl + Enter` instead of a mouse

### 

# Run this line first

```{r}
if (!require('tidyverse')) install.packages('tidyverse'); library('tidyverse') 
```

# To read a csv file
```{r}
heights <- read_csv("C:/Users/jlim13/Desktop/heights.csv") #change the path to the file
```

```{r}
View(heights)
```

# To write a csv file
```{r}
numbers <- read_csv("1,2,3\n4,5,6", col_names = c("x", "y", "z"))
```

```{r}
head(numbers)
```

```{r}
write_csv(numbers, "C:/Users/jlim13/Desktop/numbers.csv") #change path to the folder and file name 
```

# To read Excel file (.xls and .xlsx) - readxl()

```{r}
library(readxl)
```
```{r}
height2 <- read_excel("C:/Users/jlim13/Desktop/heights2.xlsx") #change the path to the file
```

```{r}
head(height2)
```

# Organizing data 
```{r}
#Run this code and see all the columns and rows in detail.
#This table represents the number of TB (Tuberculosis) cases and population per country per year are represented in a tidy format.
table1 
```

```{r}
#Run this code and see `type` column
table2 
#Why untidy? - Each variable (cases or population) must have its own column.
```

```{r}
#Run this code and see `rate` column
table3
#Why untidy? - Each value (745 or 19987071) must have its own cell.
```

```{r}
#Run this code and see `1999` and `2000` column for the number of case
table4a 
#Why untidy? - Year as a variable does not exist.
```
```{r}
#Run this code and see `1999` and `2000` column for the number of population
table4b
#Why untidy? - Year as a variable does not exist.
#Each observation must have its own row. TB cases and population in 1999 and 2000 do not exist in one row.
#Each value must have its own cell. Again, 1999 is a value for Year.
```

#Pivoting using `pivot_longer()` function - step1
```{r}
#1st parameter: The set of columns whose names are values, not variables
#2nd parameter: The name of the variable to move the column names to. Here it is `year`.
#3rd parameter: The name of the variable to move the column values to. Here it’s `cases`.

table4a %>% 
    pivot_longer(c(`1999`, `2000`), names_to = "year", values_to = "cases")

```

#Pivoting using `pivot_longer()` function - step2
```{r}
#This step is for making `population` from `table4b`

table4b %>% 
  pivot_longer(c(`1999`, `2000`), names_to = "year", values_to = "population")
```

#Pivoting using `pivot_longer()` function - step3
```{r}
#To combine two tables into one

tidy4a <- table4a %>% 
  pivot_longer(c(`1999`, `2000`), names_to = "year", values_to = "cases")

tidy4b <- table4b %>% 
  pivot_longer(c(`1999`, `2000`), names_to = "year", values_to = "population")

left_join(tidy4a, tidy4b)
```

#Pivoting using `pivot_wider()` function
```{r}
table2
```

```{r}
#1st parameter: The column to take variable names from. Here, it’s `type`.
#2nd parameter: The column to take values from. Here it’s `count`.
table2 %>%
    pivot_wider(names_from = type, values_from = count)
```

#To sum up,
#pivot_longer() makes wide tables narrower and longer, and
#pivot_wider() makes long tables shorter and wider.
