---
title: "C20_lecture"
author: "John Doe"
date: "3/28/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

# if statement and function 

-   Hands-on Assignment starts from line 18.
-   Have enough time and run the codes using RStudio before doing Hands-on Assignment
-   When you want to run code, please use `ctrl + Enter` instead of a mouse

# if Statement - basic syntax
```{r}
if (condition) {
  expression
}
```

# if Statement - basic syntax
```{r}
#write it down again




```

# if Statement
```{r}
cat <- 5

if (cat > 2) {
  print("cat is greater than 2")
}

#print function will work
```

# if Statement
```{r}
cat <- 1

if (cat > 2) {
  print("cat is greater than 2")
}

#print function won't work
```

# else Statement - basic syntax
```{r}
if (condition1) {
  expression1
} else {
  expression2
}
```

# else Statement - basic syntax
```{r}
# write it down again




```

```{r}
cat <- 1

if (cat == 2) {
  print("cat is equal to 2")
} else {
  print("cat is NOT equal to 2")
}

#else condition is TRUE
```

# else if Statement - basic syntax
```{r}
if (condition1) {
  expression1
} else if (condition2) {
  expression2
} else {
  expression3
}
```

# else if Statement - basic syntax
```{r}
# write it down again






```

# else if Statement
```{r}
cat <- 4

if (cat == 2) {
  print("cat is equal to 2")
} else if (cat == 3) {
  print("cat is equal to three")
} else {
  print("cat is NOT equal to 2 or three")
}
```

# Function - basic syntax
```{r}
# A function in R is created using the function() directive

#creation
function_name_you_want <- function(argument) {
    # Do something
}

#usage
function_name_you_want()(argument)
```

# Function with if statemnt 
```{r}
findtwo <- function(x) {
  if (x == 2)
    print("The input is two")
}
```

```{r}
findtwo(2)
```

# Function with multiple tasks
```{r}
pricefunc <- function(a) {
  print(mean(a))
  print(min(a))
  b <- mean(a) + min(a)
  print(b)
  plot(a, main = "My Price Function")
}
```

```{r}
apple <- c(42, 2321, 372, 698)

pricefunc(apple)
```