---
title: "C14_lecture"
author: "John Doe"
date: "2/21/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

# Data importing and Tidy data using `tidyverse` package (2)

-   Have enough time and run the codes using RStudio before doing Hands-on Assignment
-   When you want to run code, please use `ctrl + Enter` instead of a mouse

# Run this line first

```{r}
if (!require('tidyverse')) install.packages('tidyverse'); library('tidyverse') 
```

# To read a csv file

```{r}
grade <- read_csv("C:/Users/jlim13/Desktop/student.csv") 
#replace the path with yours
```

```{r}
head(grade, 3)
```

# To write a csv file

```{r}
numbers <- read_csv("1,2,3\n4,5,6", col_names = c("x", "y", "z"))
```

```{r}
head(numbers)
```

```{r}
write_csv(numbers, "C:/Users/jlim13/Desktop/numbers.csv") #replace the path with yours
```

# To read Excel file (.xls and .xlsx) - readxl()

```{r}
library(readxl)
```

```{r}
population <- read_excel("C:/Users/jlim13/Desktop/people.xlsx") #replace the path with yours
```

```{r}
tail(population)
```

# seperate() function

```{r}
#Run this code and see `rate` column
#Why untidy? - Each value (745 or 19987071) must have its own cell

table3
```

```{r}
table3 %>% 
  separate(rate, into = c("cases", "population")) 

# split values
```

```{r}
table3 %>% 
  separate(rate, into = c("cases", "population"), sep = "/") 

#identical outcome with `sep =` argument
```

```{r}
table3 %>% 
  separate(rate, into = c("cases", "population"), convert = TRUE) 

#from `char` to `int`

```

```{r}
table3 %>% 
  separate(year, into = c("century", "year"), sep = 2) 

#split the value of `year` column into `century` and `year` by two digits 
```

# unite() function - from multiple columns to a single column

```{r}
table5 

#`century` and `year` need to be united. 
```

```{r}
table5 %>% 
  unite(new, century, year) #see underscores in `new` column
```

```{r}
table5 %>% 
  unite(new, century, year, sep = "")
#without underscore in `new` column
```

# Dealing with explicit or implicit NA values

-   Explicit NA value: flagged with NA
-   Implicit NA value: simply not present in the data

```{r}
#run this code to make a `profit` variable

profit <- tibble(
  year   = c(2015, 2015, 2015, 2015, 2016, 2016, 2016),
  qtr    = c(   1,    2,    3,    4,    2,    3,    4),
  return = c(1.88, 0.59, 0.35,   NA, 0.92, 0.17, 2.66)
)
```

```{r}
#run this code and find one explicit NA value and one implicit NA value

profit 
```

# From implicit NA values to explicit ones using `pivot_wider()`

```{r}
profit %>% 
  pivot_wider(names_from = year, values_from = return)

#see the explict NA values
```

# From implicit NA values to explicit ones using `complete()`

```{r}
profit %>% 
  complete(year, qtr)

#see the explicit NA values
```

#From explicit NA values to implicit ones using `values_drop_na = TRUE`

```{r}
profit %>% 
  pivot_wider(names_from = year, values_from = return) %>% 
  pivot_longer(
    cols = c(`2015`, `2016`), 
    names_to = "year", 
    values_to = "return", 
    values_drop_na = TRUE
  )

# see the change from 7 rows to 6 rows
```

# To fill in the NA value with the most recent non-missing value using `fill()`

```{r}
profit %>% 
  complete(year, qtr) %>%
  fill(return) 

#find `0.35` instead of `NA` in `return` column
```
